Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-18 forecast/paper/paper.tex
Down is now 20\%

% Middle authors
\author[d]{Nat DeFries}
\author[b]{Sangwon Hyun}
\author[c,d]{Natalia L.\ Oliveira}
\author[e]{James Sharpnack}
\author[f]{Jingjing Tan}
\author[g]{Robert Tibshirani}
\author[c]{Valerie Ventura}
\author[c,d]{Larry Wasserman}

@@

Figure~\ref{fig:up_down_flat} shows histograms of the differences in WIS of the 
AR model and each indicator model, where we stratify these differences by
whether the target occurs during a period of increasing cases rates (up),
decreasing case rates (down), or flat case rates (flat). To define the
increasing period, we use the same definition we used for the hotspot task in
Table \ref{tab:analysis_tasks}.  Therefore all hotspots are ``up'', while all
non-hotspots are either ``flat'' or ``down''.  For the ``down'' scenario, we 
simply use the opposite of the hotspot definition: $Y_{\ell,t}$ decreases by
more than 25\% relative to the preceding week.

>>>>

% Middle authors
\author[d]{Nat DeFries}
\author[b]{Sangwon Hyun}
\author[c,d]{Natalia L.\ Oliveira}
\author[e]{James Sharpnack}
\author[f]{Jingjing Tang}
\author[g]{Robert Tibshirani}
\author[c]{Valerie Ventura}
\author[c,d]{Larry Wasserman}

@@

Figure~\ref{fig:up_down_flat} shows histograms of the differences in WIS of the 
AR model and each indicator model, where we stratify these differences by
whether the target occurs during a period of increasing cases rates (up),
decreasing case rates (down), or flat case rates (flat). To define the
increasing period, we use the same definition we used for the hotspot task in
Table \ref{tab:analysis_tasks}.  Therefore all hotspots are ``up'', while all
non-hotspots are either ``flat'' or ``down''.  For the ``down'' scenario, we 
simply use the opposite of the hotspot definition: $Y_{\ell,t}$ decreases by
more than 20\% relative to the preceding week.
